---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# demoWork

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/berthetclement/demoWork/branch/master/graph/badge.svg)](https://app.codecov.io/gh/berthetclement/demoWork?branch=master)
[![R-CMD-check](https://github.com/berthetclement/demoWork/actions/workflows/check-standard.yaml/badge.svg?branch=master)](https://github.com/berthetclement/demoWork/actions/workflows/check-standard.yaml)
<!-- badges: end -->

The goal of demoWork is to ...

## Installation

You can install the development version of demoWork from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("berthetclement/demoWork")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(demoWork)
## basic example code
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

